### 2022-02-11 abstract.tex
Update on Overleaf.

\begin{abstract}
    In this work, we present \acs*{CLEAVE}, a novel, completely software based framework for repeatable and scalable experimentation in \acfp*{NCS}.
    While these systems have long been a subject of both theoretical and experimental research, their inter-domain nature  has led to a wide number of task-specific approaches to research, and little work has been devoted to generalizable, repeatable, and scalable experimentation.
    We aim to tackle this gap in knowledge through an approach based on the emulation of physical plants which communicate over a real network with controllers implemented in software.
    \acs*{CLEAVE} is furthermore designed and built for the edge, using Python3 and with full compatibility with industry-standard containerization solutions.
    Although designed for single-loop emulations, the flexibility afforded by the aformentioned characteristics allow our framework to be adaptated to and employed in a multitude of more complex scenarios.

    We validate \acs*{CLEAVE} using an initial implementation of an inverted pendulum \acs*{NCS}.
    Our results showcase the utility of the tool as a repeatable, extensible, and scalable solution to \acs*{NCS} performance evaluation.
\end{abstract}

>>>>

\begin{abstract}
    As the number of cyber-physical systems rises, it becomes increasingly crucial to study \acfp*{NCS} combining control communication co-design. This nature of NCSs has led to task-specific approaches to research, creating a dearth of generalizable, repeatable, and scalable experimentation. Further, with the advent of edge computing solutions, it is of paramount importance to explore its relevance in such applications. In this work, we present \acs*{CLEAVE}, a novel, completely software-based framework for repeatable and scalable experimentation in edge native NCSs.
    Our approach is based on the emulation of physical plants communicating over a real network with software-based controllers.
    \acs*{CLEAVE} is designed and built for the edge, using Python3 and with full compatibility with industry-standard containerization solutions.
    Although designed for single-loop emulations, the flexibility afforded by the aformentioned characteristics allow our framework to be adapted to a multitude of complex scenarios.

    We validate \acs*{CLEAVE} using an initial implementation of an inverted pendulum \acs*{NCS}.
    Our results showcase the utility of the tool as a repeatable, extensible, and scalable solution to \acs*{NCS} performance evaluation and benchmarking.
\end{abstract}

### 2022-02-11 cleave.tex
Update on Overleaf.

In this section, we present and detail our \ac{CLEAVE} framework for the performance evaluation of \aclp{NCS}, with a particular focus on edge deployments.
Our design follows a virtualized emulation approach; we provide a framework for the real-time \emph{emulation} of physical control systems and the easy implementation of softwarized controllers which interact with \emph{real} networks.
In other words, \ac{CLEAVE} is a platform with an easy-to-use \ac{API} on which a multitude of \ac{NCS} types can be emulated.
This allows for great flexibility, as the core components of the \ac{NCS} can easily be switched out while maintaining the realism of the network, arguably the most complex and limiting component of edge \acp{NCS}.

The framework is distributed as \emph{free and open-source} software through the \emph{GitHub} organization of the \emph{KTH ExPECA} research group\footnote{\url{https://github.com/KTH-EXPECA/CLEAVE}}.
Furthermore, we plan to eventually provide an open library of \ac{NCS} implementations, thus making the tool even more accessible to the community.

@@

%\begin{description}[style=nextline]
%\begin{itemize}
\textbf{State Base Class}\\
\ac{ABC} with an abstract method
\mintinline{python}{advance()} which users must extend with the implementation of discrete-time emulation of the plant.
The \mintinline{python}{advance()} method is called by the framework periodically according to the configured emulation update rate, and should perform a single time-step of the discrete-time emulation.
Two optionally extensible methods, \mintinline{python}{initialize()} and \mintinline{python}{shutdown()} are provided for users to implement single-fire set-up and tear-down procedures.

@@

\textbf{Controller Base Class}\\
Defines a single abstract method \mintinline{python}{process()}, which takes a mapping of names to values corresponding to the sensed variables of the \emph{State}, and must return a similar mapping corresponding to the actuated variables.
This method is called by \ac{CLEAVE} in an event-based manner whenever samples are received from the plant side; however, we intend to extend this implementation to time-interval-based approaches.

\textbf{Sensor Base Class}\\
\emph{Sensors} implement the processing of monitored stated variables before sending them over the network to the \emph{Controller}.
This base class must be initialized with a property name (corresponding to the monitored \emph{State} attribute) and a sampling rate in \si{\hertz}, and provides an abstract method \mintinline{python}{process_sample()} which must be extended with an implementation of the processing performed on each sample.

\textbf{Actuator Base Class}\\
Finally, \emph{Actuators} perform the processing of actuation values obtained over the network from the \emph{Controller}.
The base class is initialized with a property name corresponding to the name of the actuated \emph{State} attribute, and provides two abstract methods which must be implemented by extending classes:
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
\item \mintinline{python}{set_value()}, which is called by the framework whenever a new value for the corresponding actuated attribute is received
\item \mintinline{python}{get_actuation()}, which is called on every time-step and must return a value to apply to the actuated attribute.
\end{enumerate*}
%\end{itemize}
%\end{description}

@@

Once the core components for the emulation have been defined and implemented, they need to be registered with the framework.
This is done through Python scripts which simply define a number of required (and some optional) top-level variables, corresponding to emulation parameters such as the \emph{State}, \emph{Controller}, \emph{Sensor}, and \emph{Actuator} subclasses to use; the emulation update rate; the controller-side host and address; data output directories; \emph{et cetera}.
These Python configuration files are then provided as arguments to the \texttt{cleave} command line provided by the framework.
\ac{CLEAVE} imports and parses them, and then sets up and executes the emulation.

Although the core design of \ac{CLEAVE} follows a single-loop approach, multi-loop scenarios can be easily implemented through the combination of multiple \ac{CLEAVE} instances.
Furthermore, the framework makes no assumptions about the individual components other than the signatures of methods on the base classes that must be extended and implemented.
Combined with the plain-Python emulation configuration scripts, this makes development of more complex scenarios merely a matter of implementing the desired functionality within the framework itself.

>>>>

In this section, we detail our \ac{CLEAVE} framework for the performance evaluation of \aclp{NCS}, with an emphasis on edge deployments.
Our design follows a virtualized emulation approach; providing a framework for the real-time \emph{emulation} of physical control systems and the easy implementation of softwarized controllers interacting with \emph{real} networks.
\ac{CLEAVE} is thus, a platform with an easy-to-use \ac{API} on which a multitude of \ac{NCS} types can be emulated.
This allows for great flexibility, as the core components of the \ac{NCS} can be switched out while maintaining the realism of the network, the most complex and limiting component of edge \acp{NCS}.

The framework is distributed as \emph{free and open-source} software through the \emph{GitHub} organization of the \emph{KTH ExPECA} research group\footnote{\url{https://github.com/KTH-EXPECA/CLEAVE}}.
We also plan to provide a library of \ac{NCS} implementations, making the tool even more accessible.

@@

%\begin{description}[style=nextline]
%\begin{itemize}
\textbf{State Base Class}:
\ac{ABC} with an abstract method
\mintinline{python}{advance()} which must be extended with the implementation of discrete-time emulation of the plant.
The \mintinline{python}{advance()} method is called by the framework periodically according to the configured emulation update rate, and should perform a single time-step of the discrete-time emulation.
Two optionally extensible methods, \mintinline{python}{initialize()} and \mintinline{python}{shutdown()} are provided to implement single-fire set-up and tear-down procedures.

@@

\textbf{Controller Base Class}:
Defines a single abstract method \mintinline{python}{process()}, taking a mapping of names to values corresponding to the sensed variables of the \emph{State}, and returning a similar mapping corresponding to the actuated variables.
This method is called by \ac{CLEAVE} in an event-based manner whenever samples are received from the plant side; however, we intend to extend this to time-interval-based approaches.

\textbf{Sensor Base Class}:
Implements processing of monitored stated variables before sending them over the network to the \emph{Controller}.
This base class must be initialized with a property name (corresponding to the monitored \emph{State} attribute) and a sampling rate in \si{\hertz}, and provides an abstract method \mintinline{python}{process_sample()} which must be extended with an implementation of the processing performed on each sample.

\textbf{Actuator Base Class}:
Performs the processing of actuation values obtained over the network from the \emph{Controller}.
It is initialized with a property name corresponding to the name of the actuated \emph{State} attribute, and provides two abstract methods which must be implemented by extending classes:
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
\item \mintinline{python}{set_value()}, called by the framework whenever a new value for the corresponding actuated attribute is received
\item \mintinline{python}{get_actuation()}, called on every time-step and must return a value to apply to the actuated attribute.
\end{enumerate*}
%\end{itemize}
%\end{description}

@@

Once the core components for the emulation have been defined and implemented, they need to be registered with the framework.
This is done through Python scripts which define a number of required (and some optional) top-level variables, corresponding to emulation parameters such as the \emph{State}, \emph{Controller}, \emph{Sensor}, and \emph{Actuator} subclasses to use; the emulation update rate; the controller-side host and address; data output directories; \emph{et cetera}.
These Python configuration files are then provided as arguments to the \texttt{cleave} command line provided by the framework.
\ac{CLEAVE} imports and parses them, and then sets up and executes the emulation.

Although the core design of \ac{CLEAVE} follows a single-loop approach, multi-loop scenarios can be easily implemented through the combination of multiple \ac{CLEAVE} instances.
The framework doesn't assume the individual components other than the signatures of methods on the base classes that must be extended and implemented.
Combined with the Python emulation configuration scripts, this makes development of more complex scenarios merely a matter of implementing the desired functionality within the framework itself.

### 2022-02-11 intro.tex
Update on Overleaf.

A subcategory of \acp{CPS} which stands to particularly benefit from the adoption of the above technologies is \acp{NCS}~\cite{Gupta2010NCSOverview}, a type of \ac{CPS} wherein multiple networked actuators and sensors form a part of the same automatic control system.
Depending on the physical system being controlled, \acp{NCS} can have stringent timing and reliability requirements for the communication between components that conventional cloud paradigms and cellular networks are unable to meet~\cite{Wan2020Efficient}.

Due to their potential advantages for industrial and commercial settings, a large body of work exists dedicated to the modelling and performance characterization of \acp{NCS}~\cite{Zhang2013Survey,Zhang2016Survey}.
They improve and flexibilize existing control systems by allowing for the distribution of control functions across networks, allowing for centralized coordination, control, and monitoring of a multitude of devices.

% Most of the literature concerning \acp{NCS}, follows a theoretical approach, and only a small fraction of it deals with experimental studies.
A number of works concerning \acp{NCS} deal with experimental studies.
\acp{NCS} have an inherently inter-domain nature intertwining knowledge from the fields of communications, computing, and control theory in ways that cannot be studied in isolation, leading to various different approaches to such studies.
One such approach uses setups in which the complete system is built on top of real hardware.
This approach is employed in the works of, for instance, \textcite{Li2014Wireless,Baumann2018LowPower,Cuenca2019UAV}; in all of these, the authors implement their approach on physical testbeds.
Conversely, other studies choose to instead use completely \emph{simulated} \ac{NCS} setups.
\textcite{Wu2012NPC,Chen2015synccontrol,Ma2019DynamicSched} are examples of works in which the authors have opted for such completely virtualized approaches.
These studies often employ combinations of physical and network simulation tools to try to capture the complex dynamics of \acp{NCS}.
Finally, some experimental studies instead employ \emph{virtualized} approaches, in which either
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; or }}]
    \item a real network interacts with a simulated or emulated control system~\cite{Wang2020VoltageControl}
    \item a simulated network interacts with a real control system~\cite{Natale2004InvPendEthernet}.
\end{enumerate*}

As evidenced above, experimental research in \acp{NCS} includes varied heterogeneous hardware and software platforms, methodologies and \aclp*{KPI}.

This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
This has caused a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

\textcite{Zoppi2020NCSBench} made the first (and to the best of our knowledge, the only) attempt at tackling this challenge in their work.
Their proposed platform \emph{NCSbench} is an open-source \ac{NCS} benchmarking platform, built utilizing LEGO\textregistered{}\ Mindstorms EV3 Core Set\texttrademark{}\ platform, with stated goals of reproducibility and ease of use.
It achieves them thanks to its low-cost, accessibility, and ease of reconfiguration.

Although it is an important step towards the reproducibility of \ac{NCS} benchmarks, we believe it still falls short on some aspects.
In particular, we argue the reliance on specific hardware for the Plant which although flexible, limits the benchmarking to only those systems which can be physically implemented on it.
Furthermore, it is \emph{not} scalable, and thus unsuitable for studies of larger, distributed \acp{NCS}.

In this paper, we present the first fully-software-based framework for scalable and repeatable benchmarking of edge-native \ac{NCS}.
As the edge computing paradigm starts to be adopted by industry, more and more variations of it have begun to appear in literature.
``Near'', ``far'', ``core'', and ``telco'' edge, among others, are all terms which describe variations of the original concept and which are becoming ubiquitous in new research.
While the core idea of edge computing is widely accepted as fundamental for pervasive \acp{NCS} in general, understanding the strenghts and weaknesses of such different edge concepts is of paramount importance.

Our framework, \ac{CLEAVE}, aims to simplify the repeatable and scalable benchmarking of such systems.
\ac{CLEAVE} is fully virtualized, inspired by our previous work on benchmarking human-in-the-loop applications on the edge~\cite{Olguin2019EdgeDroid}.
The tool consists of a benchmarking framework and software development kit for the development of emulated physical systems and softwarized controllers.
These virtual \acp{NCS} can then be deployed on real networks for reparametrizable, repeatable, and reproducible benchmarking of the complete system.

\ac{CLEAVE} is built using \emph{Python 3.8}, making it highly extensible and able to harness the multitude of already existing user-provided libraries.
It is furthermore compatible with container technologies such as \emph{Docker}\footnote{Docker Engine: \url{https://www.docker.com/}}, making it suitable for automated deployment, scaling, and benchmarking on industry-standard edge setups using container orchestration solutions.

The rest of this paper is structured as follows.
\cref{sec:approach} presents the design principles and implementation of the framework.
In \cref{sec:experiments}, we present a series of experiments which validate the utility, flexibility, and repeatability of \ac{CLEAVE}.
Finally, in \cref{sec:conclusion} we conclude this paper and briefly discuss future work.

>>>>

\acp{NCS}~\cite{Gupta2010NCSOverview}, a type of \ac{CPS} wherein multiple networked actuators and sensors form a part of the same automatic control system will benefit from the adoption of these technologies.
Depending on the physical system being controlled, \acp{NCS} can have stringent timing and reliability requirements for communication that conventional cloud paradigms and cellular networks can't meet\cite{Wan2020Efficient}.

There are multiple works dedicated to the modelling and performance characterization of \acp{NCS}~\cite{Zhang2013Survey,Zhang2016Survey}, improving NCSs by distributing control functions across networks, facilitating centralized coordination, control, and monitoring.

% Most of the literature concerning \acp{NCS}, follows a theoretical approach, and only a small fraction of it deals with experimental studies.
A number of works concerning \acp{NCS} deal with experimental studies.
\acp{NCS} have an inherently inter-domain nature intertwining knowledge from the fields of communications, computing, and control theory in ways that cannot be studied in isolation, leading to various different approaches to such studies.
One such approach uses setups in which the complete system is built on top of real hardware.
This approach is employed in the works of  \textcite{Li2014Wireless,Baumann2018LowPower,Cuenca2019UAV}; in all of these, the authors implement their approach on physical testbeds.
Conversely, other studies choose to instead use completely \emph{simulated} \ac{NCS} setups.
\textcite{Wu2012NPC,Chen2015synccontrol,Ma2019DynamicSched} are examples of works in which the authors have opted for such completely virtualized approaches.
These studies often employ combinations of physical and network simulation tools trying to capture the complex dynamics of \acp{NCS}.
Finally, some experimental studies instead employ \emph{virtualized} approaches, in which either
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; or }}]
    \item a real network interacts with a simulated or emulated control system~\cite{Wang2020VoltageControl}
    \item a simulated network interacts with a real control system~\cite{Natale2004InvPendEthernet}.
\end{enumerate*}

As evidenced above, experimental research in \acp{NCS} includes varied heterogeneous hardware and software platforms, methodologies and \aclp*{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.

Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
This has caused a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

\textcite{Zoppi2020NCSBench} made the first (and to the best of our knowledge, the only) attempt at tackling this challenge in their work.
Their proposed platform \emph{NCSbench} is an open-source \ac{NCS} benchmarking platform, built utilizing LEGO\textregistered{}\ Mindstorms EV3 Core Set\texttrademark{}\ platform. It is reproducible because of its low-cost and accessibility. Although important for the reproducibility of \ac{NCS} benchmarks, we believe it is still inadequate given the reliance on specific hardware for the Plant which although flexible, limits the benchmarking to only those systems which can be physically implemented.
It is \emph{not} scalable, and thus unsuitable for distributed \acp{NCS}.

In this paper, we present the first fully-software-based framework for scalable and repeatable benchmarking of edge-native \ac{NCS}.
As edge computing begins being adopted by industry, more and more variations have begun to appear in literature.
``Near'', ``far'', ``core'', and ``telco'' edge describe variations of the original concept and are becoming ubiquitous in new research.
While the core idea of edge computing is widely accepted as fundamental for pervasive \acp{NCS} in general, understanding the strenghts and weaknesses of such different edge concepts is of paramount importance.

Our framework, \ac{CLEAVE}, aims to simplify the repeatable and scalable benchmarking of such systems.
It is fully virtualized, inspired by our previous work on benchmarking human-in-the-loop applications on the edge~\cite{Olguin2019EdgeDroid}.
The tool consists of a benchmarking framework and software development kit for the development of emulated physical systems and softwarized controllers.
These virtual \acp{NCS} can then be deployed on real networks for reparametrizable, repeatable, and reproducible benchmarking of the complete system.

\ac{CLEAVE} is built using \emph{Python 3.8}, making it highly extensible and able to harness the multitude of already existing user libraries.
It is furthermore compatible with container technologies such as \emph{Docker}\footnote{Docker Engine: \url{https://www.docker.com/}}, making it suitable for automated deployment, scaling, and benchmarking on industry-standard edge setups using container orchestration solutions.

The rest of this paper is structured as follows.
\cref{sec:approach} presents the design principles and implementation of the framework.
In \cref{sec:experiments}, we present a series of experiments which validate the utility, flexibility, and repeatability of \ac{CLEAVE}.
Finally, in \cref{sec:conclusion} we conclude this work.
